\documentclass{amsart}
\usepackage[utf8]{inputenc}

\usepackage{mymacros, stmaryrd, tikz}
%\usepackage{ pstricks, pst-node, pst-text, pst-tree}
\usepackage{subfigure, epsfig, psfrag}


\usepackage[all]{xy}
\usepackage{float}
\usepackage{dynkin-diagrams}

\newcommand{\balpha}{\boldsymbol{\alpha}}
\newcommand{\bbeta}{\boldsymbol{\beta}}

\newtheorem{thm}{Theorem}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rmk}[thm]{Remark}
\newtheorem{notn}[theorem]{Notation}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{eg}[thm]{Example}

\newcommand\pgap{\vspace{10pt}}
\newcommand{\Wedge}{\mbox{\scalebox{1.2}{$\wedge$}}}
%\newcommand\to{\rightarrow}

\newcommand\isoto{\stackrel{\sim}{\longrightarrow}}


%**** Notation to be fixed  ************

\newcommand\VW{V_W}
\newcommand\W{W}
\newcommand\Y{Y}

%*****************

\title{ADE as GSM}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
Crepant resolution conjectures.
Techniques naturally extend to symplectic quotient singularities.
Blow air into the walls of the octant.
Monoidal categories result.



\section{Background}\label{sc:background}

\subsection{Quivers}
A quiver $Q$ is specified by two finite sets $Q_0$ and $Q_1$ together with two maps $h, t \colon Q_1 \rightarrow Q_0$. We call the elements of these sets vertices and arrows, respectively.  The maps $h$ and $t$ indicate the vertices at the head and tail of each arrow.
A nontrivial path in $Q$ is a sequence of arrows $p = a_1 \dotsb a_m$ with $h(a_{k}) = t(a_{k+1})$ for $1 \leq k < m$.  We set $t(p) = t(a_{1})$ and $h(p)= h(a_m)$, the length of $p$ is $m$.  
For each $i \in Q_0$ we have a trivial path $\bfe_i$ where $t(\bfe_i) = h(\bfe_i) = i$.  
The path algebra $\bfk Q$ is the $\bfk$-algebra whose underlying $\bfk$-vector space has a basis consisting of paths in $Q$; the product of two basis elements equals the basis element defined by concatenation of the paths if possible or zero otherwise.
The trivial paths $\bfe_i$ give idempotents of $\bfk Q$.

A representation $\bfx = (V_i, x_a)$ of $Q$ consists of a vector space $V_i$ for each $i \in Q_0$ and a linear map $x_a \colon V_{t(a)} \rightarrow V_{h(a)}$ for each $a \in Q_1$. 
When $\dim V_i$ is finite, the dimension vector of $\bfx$ is the integer vector $(\dim V_{i})_{i\in Q_0}$.  
A map between representations $\bfx = (V_i, x_a)$ and $\bfx' = (V_i', x_a')$ is a family $\xi_{i} \colon V_i^{\,} \rightarrow V_i'$ for $i \in Q_0$ of linear maps that are compatible with the structure maps, that is $x_a' \circ\xi_{t(a)} = \xi_{h(a)} \circ x_a$ for all $a \in Q_1$.  
With composition defined componentwise, we obtain the abelian category of representations of $Q$ denoted Rep$_\bfk(Q)$. 
This category is equivalent to the category $\bfk Q$-Mod of left-modules over the path algebra.
A relation $r$ on $Q$ is a finite linear combination of paths that share the same head and tail.
A quiver with relations is $Q$ along with a finite set of relations $R$.
A representation of a $(Q,R)$ is a representation of $Q$ for which $x_r=0$ for all $r\in R$.
Representations of $(Q,R)$ correspond to left-modules of $\bfk Q/ \langle R \rangle$.

Given a dimension vector $\bfd$, a $\theta \in \bZ^{Q_0}$ for which $\bfd \cdot \theta=0$ defines a stability notion for representations of $Q$ with dimension vector $\bfd$.
A representation $\bfx$ is $\theta$-semistable if, for every proper, nonzero subrepresentation $\bfx' \subset \bfx$, we have $\sum_{i \in Q_0} \theta_i \cdot \dim(V_i') \geq 0$.  
The notion of $\theta$-stability is obtained by replacing $\geq$ with $>$. 
For a given dimension vector $\bfd =(d_i)_{i \in I} \in \bZ_{Q_0}$, a family of $\theta$-semistable quiver representations over a connected scheme $S$ is a collection of rank $d_i$ locally free sheaves $\cV_i$ together with morphisms $\cV_{t(a)} \rightarrow \cV_{h(a)}$ for every $a\in Q_1$. 
When every $\theta$-semistable representation is $\theta$-stable and the dimension vector is primitive this moduli problem is representable by a smooth scheme $\cM^\theta(Q, \bfd)$, see Proposition 5.3 in \cite{Ki}.
The scheme $\cM^\theta(Q, \bfd)$ comes with a universal family $(\cV_i, \cV_{t(a)} \rightarrow \cV_{h(a)})_{i \in Q_0, a \in Q_1}$. 
We may define analogous notions for quivers with relations, we will denote the corresponding moduli spaces by $\cM^\theta(Q,R,\bfd)$.

The space $\cM^\theta(Q, \bfd)$ may be expressed as a quotient stack.
Pick vector spaces $V_i$ of dimension $d_i$.
Every point of the affine space
$$\cS:= \bigoplus_{a \in Q_1} \Hom(V_{t(a)}, V_{h(a)})$$
defines a representation of $Q$ with dimension vector $\bfd$.
We write $\cS^\theta$ for the open subvariety of points corresponding to $\theta$-semistable representations.
Change of basis gives a group action of $\GL(\mathbf{d}):= \oplus_{i \in Q_0} \GL(V_i)$ on $\cS$.
The multiplicative group $\bG_m$ diagonally embeds in $\GL(\mathbf{d})$ and acts trivially on $\cS$.
Therefore the action of $\GL(\mathbf{d})$ descends to an action of $\Gamma_\bfd:= \GL(\mathbf{d})/\bG_m$ on $\cS$ and we have $\cM^\theta(Q, \bfd) = [\cS^\theta / \Gamma_\bfd].$
Given a set of relations $R$, restricting to the closed set of points $\cS$ whose corresponding quiver representations respect the relations gives a closed subset of $\cR \subset \cS$ and $$\cM^\theta(Q,R,\bfd)= [\cR^\theta/\Gamma_\bfd].$$

\subsection{The McKay correspondence}\label{ssc:McKay}
Not only is this an abridged version of a rich story but we also spin it here to motivate what follows.
Fix a finite subgroup $G \subset \SL(2,\bC)$ and let $\rho_0, \ldots, \rho_N$ be its
irreducible representations with $\rho_0$ being the trivial representation.
Set $I=\{0,\ldots,N\}$.
We write $\W$ for the defining representation of $G$.

\subsubsection{The McKay quiver}
The monoidal category $\Rep(G)$ is semi-simple therefore $$\rho_i \otimes_G \W \simeq \bigoplus_{j \in I} c_{ij} \, \rho_j$$
with $c_{ij} =\dim \Hom_{\bC G}(\rho_i \otimes_G \W, \rho_j)$.
The numbers $c_{ij}$ allow us to define the {\em McKay quiver} $Q$: the vertices are indexed by irreducible representations labelled by $I$ with $c_{ij}$  arrows from $i$ to $j$.
The defining representation $\W$ is self-dual hence $c_{ij} = c_{ji}$.
%The defining representation $\W$ is self-dual, fixing an isomorphism $\alpha_0 \colon \W \rightarrow \W^\vee$ allows us to define a bijection between arrows with head at a vertex $i$ with those with tail at $i$; in particular $c_{ij} = c_{ji}$.
It is therefore possible to unambiguously define a graph associated to $Q$ with vertex set $I$ and $c_{ij}$ edges between $i$ and $j$. This is the McKay graph associated to $G$.

\begin{theorem}\cite{MR604577}.
The McKay graph associated to $G \subset \SL(2,\bC)$ is an affine Dynkin diagram of type $\widetilde{A}\widetilde{D}\widetilde{E}$.
Moreover, the subgraph given by removing the vertex $0$ is the corresponding $ADE$ Dynkin diagram.
\end{theorem}

We identify an arrow $i \rightarrow j$ with a morphism of representations $\beta_{i \rightarrow j} \colon \rho_i \otimes_G \W \rightarrow \rho_j$.
For every irreducible representation this gives us isomorphisms 
\begin{align}
    \beta_i &\colon \rho_i \otimes_G \W \longrightarrow \bigoplus_{i \rightarrow j} \rho_j \\
    \beta^i &\colon \rho_i^\vee \otimes_G \W \longrightarrow \bigoplus_{i \rightarrow j} \rho_j^\vee.
\end{align}
We may choose, and do choose, $\beta_{i \rightarrow j}$ so that $\beta_i^{-1} = \alpha_0^{-1} \circ (\beta^i)^\vee$ up to our fixed isomorphism $\alpha_0 \colon \wedge^2 \W \rightarrow \bC$.
The isomorphism $\alpha_0$ may also be interpreted as an isomorphism $\alpha_0 \colon W \rightarrow W^\vee$.
This, in turn, gives an involution $\iota$ on the arrows of $Q$ sending $\beta_{i \rightarrow j}$ to its dual under the symplectic pairing given by 
$$\rho_i \otimes \W \xrightarrow{\beta_i} \bigoplus_{i \rightarrow j} \rho_j  \xrightarrow {(\beta^i)^\vee} \rho_i \otimes \W^\vee \xrightarrow{\text{id} \otimes \alpha_0} \rho_i \otimes \W.$$

%TO DO: I'M CONFUSED BY THE ABOVE, WHAT'S IT FOR? SHOULD WE JUST FIX $\det W\cong \bC$?

The morphisms $\beta_{i \rightarrow j}$ give a natural isomorphism of vector spaces $$\Hom_{\bC G}(\rho_i \otimes_G \W^{\otimes n}, \rho_j) \simeq \langle\, \text{paths of length }n \text{ from }i \text{ to } j\,\rangle.$$
In particular, for a vertex $i$, the one-dimensional space $\Hom_{\bC G} (\rho_i \otimes \det \W, \rho_i)$ gives, up to $\alpha_0$, a relation $r_i$ of length 2 from $i$ to itself.
The set $R = \{r_i \, |\, i \in I\}$ makes $Q$ into a quiver with relations $(Q, R)$. 
We take $\cA:= \bk Q/ \langle R\rangle$.
On the other hand, the action of $G$ on $\W$ induces an action on the symmetric algebra $S(W^\vee)$ which is related to $\cA$ by the following result.

\begin{theorem}\cite{MR2593679}.
The skew-group algebra $S(W^\vee) \# G$ is Morita equivalent to $\cA$.
\end{theorem}

\subsubsection{The $G$-Hilbert scheme}

The invariant ring of the $G$-action on $S(W^\vee)$ will be denoted $S(W^\vee)^G \subset S(W^\vee)$, it is the centre of $S(W^\vee) \# G$ and is isomorphic to the subring $\bfe_0 \cA \bfe_0 \subset \cA$.
The variety $X:= \Spec(\bfe_0 \cA \bfe_0)=\W/G$ parametrises the orbits of the $G$-action on $\W$ and has a singularity at the $0$-orbit.
The variety $X$ is Gorenstein, that is it is Cohen-Macaulay and its dualizing sheaf $\omega_X$ is invertible.
The $G$-Hilbert scheme, $G$-Hilb($\W$), parametrises scheme theoretic orbits of $G$ i.e.\ $G$-equivariant ideals $I$ of $S(W^\vee)$ for which $S(W^\vee)/I \simeq \bC G$ as $\bC G$-modules.
The Hilbert-Chow morphism $\pi \colon G\text{-Hilb}(\W) \rightarrow X$ takes the zero-locus of $I \subset S(W^\vee)$ to its corresponding $G$-orbit.
Furthermore, $\pi \colon G\text{-Hilb}(\W) \rightarrow X$ is a crepant resolution of singualrities, in other words it is a resolution with $\pi^*\omega_X \simeq \omega_{G\text{-Hilb}(\W)}$.

\begin{theorem}\cite{MR604577}.
The inverse image of the singular point $\pi^{-1}(0)$ is a tree of transversely intersecting $\bP^1$s whose intersection graph is dual to the $ADE$ Dynkin diagram corresponding to $G$.
\end{theorem}

%The $G$-Hilbert scheme on $V$ is may be constructed as a moduli of quiver representations of the McKay quiver with relations $(Q,R)$.
Take $\cM^\vartheta:=\cM^\vartheta(Q,R,\bfd)$ for $\vartheta = (-|G|,1, \ldots, 1)$ and $\bfd=(\text{rank}(\rho_i))_{i \in I}$, we have an isomorphism $\cM^\vartheta \simeq G\text{- Hilb}(\W)$.

\begin{theorem}\cite{MR740077}, \cite{MR1752785}.
There is an equivalence of triangulated categories $$\Phi \colon D^b(\cM^\theta) \longrightarrow D^b(\cA)$$ that takes the universal bundle $\cV_i$ to the projective $\cA$-module $\cA\bfe_i$.
\end{theorem}

\section*{Notation}
We fix the following notation for the rest of the text:
\pgap

\begin{centering}
\begin{tabular}{r l}
    $G \subset \SL(2,\bC)$ & a finite subgroup acting with no pseudo-reflections. \\
    $\W$ & the defining representation of $G$ on $\bC^2$. \\
    $\rho_0, \ldots, \rho_N$ & the irreducible representations of $G$ with $\rho_0$ trivial. \\
    $I$ & the set $\{0,\ldots,N\}$.  \\
    $X$ & the singular affine quotient $\Spec(S(\W^\vee)^G) = \W/G$. \\
    $\bX$ & the smooth stack quotient $[\W/G]$. \\
    $(Q,R)$ & the McKay quiver with relations. \\
    $\cA$ & the algebra $\bk Q/ \langle R\rangle$. \\
    $P_i$ & the projective module $\cA\bfe_i$ corresponding to the vertex $i$. \\
    $\bfd=(d_0,..., d_N)$ & the vector of dimensions $d_i=\text{rank}(\rho_i)$. \\
    $V_i$ & a vector space of dimension $d_i$. \\
    $L_i$ & the determinant $\Wedge^{d_i} V_i$. \\
     $\Gamma$ & the group $\bigoplus_{i \in I} \text{GL}(V_i) / \bG_m$. \\
    $\cS$ & the vector space $\bigoplus_{a \in Q_1} \Hom(V_{t(a)}, V_{h(a)})$. \\
  $\cR\subset \cS$ & the subvariety where the relations hold. \\
    $\cM$ & the stack quotient  $\cM(Q,R,\bfd)=[\cR/\Gamma]$. \\
    $\cM^\theta$ & the stack quotient $\cM^\theta(Q,R,\bfd)=[\cR^\theta/\Gamma]$ given $\theta \in \bZ^{Q_0}$. \\
    $\vartheta$ & the stability parameter $(-|G|,1, \ldots, 1) \in \bZ^{Q_0}$. \\
   $\VW$ & the direct sum of $V_i$ corresponding to $W$. \\
    $L_W$ & the determinant $\Wedge^2 \VW$. \\
    \end{tabular}
\end{centering}
 
The final two items may need a little clarification. In type $A$ the representation $W$ splits as $\rho_1\oplus \rho_N$ so $V_W$ is shorthand for $V_1\oplus V_N$. In types $D$ and $E$ the representation $W$ is one of the two-dimensional irreps $\rho_i$ and $V_W$ denotes the corresponding $V_i$.  Note that $\Wedge^2 W$ is a trivial representation of $G$ but $L_W=\Wedge^2\VW$ is not a trivial representation of $\Gamma$. 

Finally we fix an isomorphism  $V_0\simeq \bC$ and, in turn, an isomorphism $\Gamma\simeq \bigoplus_{i>0} \text{GL}(V_i)$.

\section{The construction}

In this section we define an affine variety $\Y$ with an action of $\Gamma$. In subsequent sections, GIT will be used to construct a quotient of $\Y$ which is isomorphic to $\bX$ and another which isomorphic to $G$-Hilb$(\bC^2)$.
We begin by describing $\Y$ as a closed subset of an affine space $\bA$.

\subsection{The fields}
Our affine space $\bA$ is defined as
\begin{equation*}
    \VW \oplus \bigoplus_{i>0} \Hom\Big(L_i^{\otimes 2},\, \bigotimes_{i \rightarrow j} L_j\Big) \oplus  \bigoplus_{\substack{a\in Q_1\\t(a)\neq 0}} \Hom\Big(V_{t(a)} \otimes \VW,\,  V_{h(a)}\Big) 
\end{equation*}
Points in $\bA$ are given by a tuple $(\bfx,\balpha, \bfB)$ as described below:
\begin{align}
\bfx \colon &V_0 \longrightarrow \VW \label{fd:x} \\
\alpha_i \colon &L_i^{\otimes 2}\longrightarrow \bigotimes_{i \rightarrow j} L_j  \label{fd:alpha}\quad\mbox{for }i>0 \\
B_{i \rightarrow j} \colon &V_i \otimes \VW \longrightarrow V_j  \label{fd:B}\quad\mbox{for }(i \rightarrow j) \in Q_1. 
\end{align}

The $\alpha_i$ are scalars. 
It sometimes helps to group the fields $B_{i \rightarrow j}$ using either the tail or head vertex as below:

\begin{notn}\label{notn:B^i}
Fix $i>0$. 
We sum over arrows with tail at $i$ to form
\begin{align*}
B_i = \sum_{i \rightarrow j} B_{i \rightarrow j}:\; V_i\otimes\VW \longrightarrow\bigoplus_{i\to j} V_j.
\end{align*}
For arrows with head at $i$, we reinterpret each $B_{j \rightarrow i}$ as a map
$$ V_{i}^\vee\otimes \VW \longrightarrow V_{j}^\vee $$
and sum
\begin{align*}
B^i = \sum_{j \rightarrow i} B_{j \rightarrow i}:\; V_i^\vee \otimes \VW \longrightarrow \bigoplus_{j\to i} V_j^\vee.
\end{align*}
\end{notn}

\begin{remark}
Since every arrow has a tail, the data of $\bfB$ is equivalent to the data in the fields $B_i$ for all $i>0$.
\end{remark}

From the definition of the McKay quiver the dimensions $d_i$ satisfy
\begin{equation*}\label{eq:drelation} 2d_i = \sum_{i\rightarrow j} d_j = \sum_{j\rightarrow i} d_j \end{equation*}
so both $B_i$ and $B^i$ are `square matrices', \emph{i.e.}~maps between two vector spaces of the same dimension.
\begin{remark}\label{rm:Tannaka}
This choice of $\alpha_i$ and $B_i$ can be understood from the Tannakian approach as explained in Section \ref{sc:Tannaka}.  In the category of $G$-representations we have isomorphisms
$$\rho_i\otimes W \simeq \bigoplus_{i\to j} \rho_j$$
and (by taking the determinant of the above)
$$ (\det \rho_i)^{\otimes 2} \simeq \bigotimes_{i\to j} \det \rho_j. $$
The fields $B_i$ and $\alpha_i$ are the corresponding linear maps.
\end{remark}

\begin{remark}\label{rm:cartan}
The weights of the $\Gamma$-action on the fields $\alpha_i$ are given by minus the Cartan matrix of the corresponding Dynkin diagram.
\end{remark}

In what follows we manipulate the data $(\bfx, \balpha, \bfB) \in \bA$ in various ways; the rest of this subsection sets up the notation required.

\begin{notn}
By the definition of the McKay quiver we have
\begin{equation}\label{eq:from0} \VW = \bigoplus_{0\to j} V_j. \end{equation}
Armed with the fixed isomorphism $V_0 \simeq \bC$, we use $$B_0 \colon V_0\otimes V_W \longrightarrow\bigoplus_{0\to j} V_j$$ to denote the identity morphism. 
\end{notn}

\begin{notn}
%Grouping the linear maps $\alpha_i$ and respectively $B_i$ into big linear maps we write: 
%\begin{align*}
%\balpha &:= \bigoplus_{i\in Q_0} \alpha_i \colon \bigoplus_{i\in Q_0} L_i \otimes L_i \longrightarrow \bigoplus_{i \in Q_0} \Big( \bigotimes_{i \rightarrow j} L_j \Big) \\
%\bfB &:= \bigoplus_{i\in Q_0} B_i \colon \bigoplus_{i\in Q_0} V_i \otimes \VW \longrightarrow \bigoplus_{a \in Q_1} V_{h(a)}
%\end{align*}
%Again, using adjuctions appropriately, the morphism $\bfB$ naturally induces a linear map:
We can reinterpret each $B_i$ as a map
$$ \VW \longrightarrow \bigoplus_{i\to j} \Hom( V_i,  V_j). $$
Adding these together (including $B_0=\id_{\VW}$) we get a linear map
$$\widetilde{\bfB} :\; \VW \longrightarrow\; \cS \,\,=\bigoplus_{i\to j} \Hom(V_i, V_j).$$
\end{notn}

This is an important second perspective on our $B$ fields, complementary to the one in Remark \ref{rm:Tannaka}.
They are points in the affine subspace of $\Hom(\VW, \cS)$ where the first component is the identity.
This is an especially cool reinterpretation of the fields $B_i$ given that points of $\cS$ define representations of the quiver $Q$.

This point of view enables us to naturally associate a $Q$-representation $\widetilde{\bfB}(\bfx)$ to a point $(\bfx, \balpha, \bfB) \in \bA$ by applying $\widetilde{\bfB} \in \Hom(\VW, \cS)$ to $\bfx \in \VW$.
Given an arrow $i\to j$, the linear map $V_i \rightarrow V_j$ in the representation $\widetilde{\bfB}(\bfx) \in \cS$ is the composite
\begin{equation}\label{eq:Btilde}
 V_i \xrightarrow{\textup{id} \otimes \bfx} V_i \otimes \VW \xrightarrow{B_{i\to j}} V_j.
\end{equation}

Our final piece of notation introduces a scalar field which will be particularly important.

\begin{notn}
We let $\alpha_0$ denote the scalar field 
$$\alpha_0:= \bigotimes_{i>0} \,\alpha_i^{d_i} \colon L_W \longrightarrow \bC.$$
Since $L_W=\Wedge^2 \VW$ this is a two-form on $\VW$.

NOTE: THIS WOULD NOT BE TRUE IN THE HIGHER DIM SYMPLECTIC CASE
\end{notn}
To see why this product of $\alpha_i$'s does indeed lie in $L_W^{-1}$, observe that its target can be written as
$$ \bigotimes_{\substack{i>0 \\ i\to j}} L_j^{\otimes d_i} = \bigotimes_{i\to j} L_j^{\otimes d_i}  \otimes\bigotimes _{0\to j} L_j^{-1}.$$
The first factor is $\bigotimes_{j} L_j^{\otimes 2d_j}$ by \eqref{eq:drelation} and the second factor is $L_W^{-1}$ by \eqref{eq:from0}.  


\begin{remark} Formally extending the definition \eqref{fd:alpha} to $i=0$ suggests that $\alpha_0$ should be a map from $L_0^{\otimes 2}\simeq \bC$ to $L_W$, but our $\alpha_0$ goes in the other direction. 
\end{remark}




\subsection{The equations}
Here we describe the equations cutting out $\Y$ in $\bA$. They all involve the interplay between the maps $B_i$ and the maps $B^i$ from Notation \ref{notn:B^i}, and the scalars $\alpha_i$. 

The field $B_i$ is a map from $V_i\otimes \VW$ to $\bigoplus_{i\to j} V_j$, and if we dualize the map $B^i$ we get a map
$$(B^i)^\vee: \bigoplus_{j \to i} V_j \longrightarrow V_i\otimes \VW^\vee.$$
As discussed in Section~\ref{ssc:McKay}, the McKay quiver has an involution on its set of arrows, sending an arrow $a:i\to j$ to a dual arrow $a':j\to i$.
%The target of $B_i$ and the source of $(B^i)^\vee$ are identical, because the self-duality of the representation $\W$ gives us a bijection between arrows $i \to j$ in $Q$ and arrows to $j \to i$. 
This induces, for each vertex $i$, an isomorphism
$$ \Omega_i: \bigoplus_{i\to j} V_j \isoto \bigoplus_{j\to i} V_j. $$
So we can form the composite 
$$(B^i)^\vee\circ\Omega_i\circ B_i :\; V_i \otimes \VW \longrightarrow V_i\otimes \VW^\vee.$$
The scalar $\alpha_0\in \Wedge^2 \VW^\vee$ may be throught of as a map from $\alpha_0 \colon \VW \rightarrow \VW^\vee$. Our first set of equations are
\begin{equation}\label{eq:rel1}
\boxed{\quad (B^i)^\vee\circ\Omega_i\circ B_i  = \id_{V_i} \otimes \alpha_0. \quad}
\end{equation}

%We need more notation to do so.

%\begin{notn}
%We have natural isomorphisms
%$$\Omega_r(V) \colon \wedge^{d+r} V \rightarrow \wedge^{d-r} V^\vee \otimes L_V$$ for $V$ a $2d$-dimensional vector space and $r= -d, \ldots, d$.
%We will drop the vector space $V$ and the subscript $r$ from $\Omega_r(V)$ when it is clear from the context.

For our second set of equations, we recall that for any vector space $U$ we have a natural isomorphism 
$$\Wedge^{(\dim U -s)}\, U = \Wedge^s U^\vee \otimes \det U $$
for all $s$.  The map $B^i$ is a map between two vector spaces each of which have dimension $2d_i$. Consider the wedge power
$$\Wedge^{d_i-r} B^i: \; \Wedge^{d_i-r}\big( V_i^\vee\otimes \VW \big) \longrightarrow \Wedge^{d_i-r} \Bigg( \bigoplus_{j\to i} V_j^\vee \Bigg) $$
for some $0\leq r \leq d_i$. The source of this map is naturally isomorphic to
$$ \Wedge^{d_i+r} \big( V_i \otimes \VW^\vee \big) \otimes \det \big( V_i^\vee\otimes \VW \big) \; \cong\; 
  \Wedge^{d_i+r} \big( V_i \otimes \VW \big) \otimes L_i^{-2}\otimes L_W^{-r} $$
and its target is naturally isomorphic to
$$\Wedge^{d_i+r} \Bigg( \bigoplus_{j\to i} V_j \Bigg)\otimes \bigotimes_{j\to i} L_j^{-1}. $$
So up to a line bundle, $\wedge^{d_i-r} B^i$ has the same source and target as the map $\wedge^{d_i+r} B_i$. 

We can correct for this line bundle using the appropriate combination of our scalar fields. Inspecting the above, the line bundle is 
$$ L_i^{-2}\otimes L_W^{-r} \otimes \bigotimes_{j\to i} L_j $$
and the scalar $\alpha_0^r\alpha_i$ is a section of this line bundle. So the equation
\begin{equation}\label{eq:rel2}
\boxed{\quad \Wedge^{d_i+r} B_i  = \alpha_0^r \alpha_i\, \Wedge^{d_i-r} B^i \quad }
\end{equation}
makes sense.

For a chosen $i$, we highlight the two extreme cases are $r=0$ and $r=d_i$ and they say
\begin{equation}\label{eq:r=0}\Wedge^{d_i} B_i = \alpha_i\Wedge^{d_i} B^i 
\end{equation}
and
\begin{equation}\label{eq:r=di} \det B_i = \alpha_0^{d_i}\alpha_i
\end{equation}
respectively. 

% Let us abuse notation by writing 
%$$\alpha_0^r \alpha_i^{-1} := \alpha_1^{rd_1} \cdots \alpha_i^{rd_i-1} \cdots \alpha_N^{rd_N}$$
%for  when $r\geq 1$ even though $\alpha_i$ is not invertible in general.
%\end{notn}

\begin{definition}\label{def:equa}
The closed subvariety $\Y \subset \bA$ is defined as the locus satisfying the equation \eqref{eq:rel1} for all $i\in I$ and the equation \eqref{eq:rel2} for all $i>0$ and all $0\leq r\leq d_i$.
\end{definition}

These equations may not be easy to understand at first sight, we'll spend the remainder of this section expanding on their meaning. Our first two lemmas are consequences of the first equation \eqref{eq:rel1}.

\begin{lemma}\label{lem:rela}
For $(\bfx, \balpha, \bfB) \in \Y$ 
% the following diagram commutes:
% \begin{equation}\label{eq:comdiag}
%     \xymatrix{V_i \otimes \VW \ar[r]^-{B_i} \ar[d]^{\textup{id}} & \big(\bigoplus_{i \rightarrow j}  V_j\big) \ar[r]^-{\Omega\,(B^i)^T \, \Omega} & V_i \otimes \VW^\vee \ar[d]^{\textup{id}} \\
%     V_i \otimes \VW \ar[r]^-{\textup{id} \otimes \Omega} & V_i \otimes \VW^\vee \otimes L_W \ar[r]^-{\textup{id} \otimes \alpha_0} & V_i \otimes \VW^\vee.}
% \end{equation}
% In particular, 
the $Q$-representation $\widetilde{\bfB}(\bfx)$ lies in the subvariety $\cR\subset \cS$ defined by the relations $R$ on $Q$, \emph{i.e.}~$\widetilde{\bfB}(\bfx)$ is a representation of $\cA$. 
\end{lemma}

\begin{proof}
For each vertex $i\in I$, \eqref{eq:rel1} implies that the composite
\begin{equation}\label{eq:inR}
    V_{i} \xrightarrow{\textup{id} \otimes \bfx} V_{i} \otimes \VW \xrightarrow{B_{i}} \bigoplus_{i \rightarrow j} V_j \xrightarrow{\Omega_i} \bigoplus_{j \rightarrow i} V_j \xrightarrow{(B^i)^\vee} V_{i} \otimes \VW^\vee \xrightarrow{\textup{id} \otimes \bfx^T} V_i
\end{equation}
is the identity map times $\alpha_0(\bfx,\bfx)$. This is zero since $\alpha_0$ is anti-symmetric. But from \eqref{eq:Btilde} this is also the sum, over all arrows $a$ with tail at $i$, of 
$$ V_{i} \xrightarrow{\widetilde{\bfB}(\bfx)_a} V_{j} \xrightarrow{\widetilde{\bfB}(\bfx)_{a'}} V_{i}  $$
where $a'$ is the dual arrow to $a$. The relations on $Q$ are that these sums vanish.
\end{proof}

% The diagram commutes since $$\wedge^{2d_i-1} B_i = \alpha_0^{d_i-1} \alpha_i \circ \Omega \circ B^i \circ \Omega^{-1}$$
% and $\det B_i= \alpha_0^{d_i} \alpha_i$.
%The commutativity of this diagram in Equation~(\ref{eq:comdiag}) implies that the composite 
%\begin{equation}\label{eq:inR}
  %  V_{i} \xrightarrow{\textup{id} \otimes \bfx} V_{i} \otimes \VW \xrightarrow{B_{i}} \bigoplus_{i \rightarrow j} V_j \xrightarrow{(\Omega\,B^i \, \Omega)^T} V_{i} \otimes \VW^\vee \xrightarrow{\textup{id} \otimes \bfx^T} V_i
%\end{equation}
%$$V_i \xrightarrow{\textup{id} \otimes \bfx \otimes \bfx} V_i \otimes \VW \otimes \VW \xrightarrow{\textup{id} \otimes \det} V_i \otimes L_W \xrightarrow {\alpha_0} V_i$$
%coincides with
%$$V_i \xrightarrow{\textup{id} \otimes \bfx} V_i \otimes \VW \xrightarrow{\textup{id} \otimes \Omega} V_i \otimes \VW^\vee \otimes L_W \xrightarrow{\textup{id} \otimes \alpha_0} V_i \otimes \VW^\vee \xrightarrow {\textup{id} \otimes \bfx^T} V_i$$ 
%which is $0$ since $\Omega$ is anti-symmetric.
%Composing the linear maps in (\ref{eq:inR}) differently we get $$V_i \longrightarrow \bigoplus_{i \rightarrow j} V_j \longrightarrow V_i$$
%is 0 and hence the relation $r_i$ holds.
%{\red May need to rewrite $r_i$ so that this is obvious.}
%\end{proof}

\begin{lemma}\label{lem:symp2}
For $(\bfx, \balpha, \bfB) \in \Y$ the map $\widetilde{\bfB}: \VW \to \cS$ intertwines the natural symplectic form $\Omega$ on $\cS$ with the two-form $(N+1)\alpha_0$ on $\VW$.
\end{lemma}

\begin{proof}
The claim is that the composite
\begin{equation}
    \VW \xrightarrow{\widetilde{\bfB}} \bigoplus_{a \in Q_1} \Hom(V_{t(a)}, V_{h(a)}) \xrightarrow{\Omega} \bigoplus_{a \in Q_1} \Hom(V_{h(a)}, V_{t(a)}) \xrightarrow{\widetilde{\bfB}^T} \VW^\vee.
\end{equation}
coincides with $(N+1)\alpha_0$. The equation \eqref{eq:rel1} implies that the composite
\begin{equation}
    \VW \xrightarrow{B_i} \bigoplus_{i \rightarrow j} \Hom(V_i, V_{j}) \xrightarrow{\Omega_i} \bigoplus_{j \rightarrow i} \Hom(V_{j}, V_{i}) \xrightarrow{(B^i)^\vee} \VW^\vee.
\end{equation}
equals $\alpha_0$, and summing over $i$ gives the result.
\end{proof}

% for which the following commutative diagrams commutes:
%\begin{equation}\label{eq:cons1}
  %  \wedge^{d_i+r} B_i = \alpha_0^r \alpha_i \circ \Omega \circ \wedge^{d_i-r} B^i \circ \Omega^{-1}
%\end{equation}
%\begin{equation}\label{eq:cons2}
%\begin{gathered}
 %   \xymatrix{\bigwedge^{r} \Big(V_i \otimes \VW\Big) \ar[rr]^-{\wedge^r B_i} \ar[d]^{\textup{id}} && \bigwedge^r \Big(\bigoplus_{i \rightarrow j}  V_j\Big) \ar[rr]^-{\Omega\,\,(\wedge^{r} B^i)^T \,\, \Omega} && \bigwedge^r \Big(V_i \otimes \VW^\vee\Big) \ar[d]^{\textup{id}} \\
 %   \bigwedge^r \Big(V_i \otimes \VW\Big) \ar[rrrr]^-{\textup{id} \otimes \alpha_0^r}
    %\ar[r]^-{\textup{id} \otimes \Omega} & V_i \otimes \VW^\vee \otimes L_W \ar[r]^-{\textup{id} \otimes \alpha_0^r} & 
   % &&&& \bigwedge^r \Big(V_i \otimes \VW^\vee\Big).}
   % \end{gathered}
%\end{equation}
%for $i\in I$ and $r=0,\ldots,d_i$.
% \begin{align}
%     \wedge^{d_i+r} B_i &= \alpha_0^r \alpha_i \circ \Omega_r(V_i \otimes \VW) \circ \wedge^{d_i-r} B^i \circ \Omega_r(\oplus V_j)^{-1}  \label{eq1:cons2} \\
%     \wedge^{d_i} B_i &= \alpha_i \circ \Omega_{0}(V_i \otimes \VW) \circ \wedge^{d_i} B^i \circ \Omega_{0}(\oplus V_j)^{-1} \label{eq2:cons2} \\
%     \alpha_0^r \alpha_i^{-1} \circ \wedge^{d_i-r} B_i &= \Omega_{-r}(V_i \otimes \VW) \circ \wedge^{d_i+r} B^i \circ \Omega_{-r}(\oplus V_j)^{-1} \label{eq3:cons2}
% \end{align}
%\end{definition}

%The relations are a mouthful.
%The most important are Equation~(\ref{eq:cons1}) with $r=0$ and Equation~(\ref{eq:cons2}) with $r=1$.
%We rewrite it here for emphasis and because we will use them often in what is to come:
%\begin{equation}\label{eq2:cons2}
 %   \wedge^{d_i} B_i =  \alpha_i \circ \Omega \circ \wedge^{d_i} B^i \circ \Omega^{-1}
%\end{equation}
%\begin{equation}\label{eq:comdiag}
%\begin{gathered}
%    \xymatrix{V_i \otimes \VW \ar[r]^-{B_i} \ar[d]^{\textup{id}} & \big(\bigoplus_{i \rightarrow j}  V_j\big) \ar[r]^-{(\Omega\,B^i \, \Omega)^T} & V_i \otimes \VW^\vee \ar[d]^{\textup{id}} \\
%    V_i \otimes \VW \ar[r]^-{\textup{id} \otimes \Omega} & V_i \otimes \VW^\vee \otimes L_W \ar[r]^-{\textup{id} \otimes \alpha_0} & V_i \otimes \VW^\vee.}
 %   \end{gathered}
%\end{equation}




% \begin{lemma}\label{lem:symp1}
% If $\alpha_0$ is invertible the fields $B_i$ are isomorphisms and the relations imply that they are `symplectic', i.e.
% \begin{equation}\label{eq:B^-1}
%     B_i^{-1} = \alpha_0^{-1} \circ \Omega_{d_i-1}(V_i \otimes \VW) \circ (B^i)^T \circ \Omega_{d_i-1}(\oplus V_j)^{-1}.
% \end{equation}
% \end{lemma}

% \begin{proof}
% Follows from the commutative diagram in Equation~\ref{eq:cons2} with $r=1$.
% \end{proof}

The following lemma relates the relation in \eqref{eq:rel1} to the relations in \eqref{eq:rel2}.

\begin{lemma}
If $\alpha_0$ is invertible, relation \eqref{eq:rel1} is equivalent to the equation
$$\Wedge^{d_i-r} B_i  = \alpha_0^{-r} \alpha_i\, \Wedge^{d_i+r} B^i$$
for $i\in I$ and $r=0,\ldots,d_i$.
\end{lemma}

\begin{proof}
Assume $\alpha_0$ is invertible.
The assumption gives that the fields $\alpha_i$ are then also invertible for all $i$ by definition of $\alpha_0$.
The determinant of $B_i$ as given \eqref{eq:r=di} is a product of fields $\alpha_i$ and so $B_i$ is also invertible in this case.
Equation \eqref{eq:rel1} then gives an expression for the inverse of $B^i$ which may also be expressed as $\wedge^{2d_i-1} B^i \otimes (\det B^i)^{-1}$.
Putting these two expressions together gives the result for $r=d_i-1$.
The wedge products follow from this case.
\end{proof}


% \begin{proof}
% The linear map $\alpha_0$ has a one-dimensional domain and codomain, therefore it is invertible if and only if it is non-zero.
% So if $\alpha_0$ is invertible then by definition $\alpha_i$ is also invertible for all $i$.
% Equation~(\ref{eq1:cons2}) with $r=d_i$ translates to $\det B_i= \alpha_0^{d_i} \alpha_i$.
% The inverse of $B_i$ is then given by $(\wedge^{2d_i-1}B_i)^T \otimes (\det B_i)^{-1}$.
% Equation~(\ref{eq1:cons2}) with $r=d_i-1$ is $$\wedge^{2d_i-1} B_i = \alpha_0^{d_i-1} \alpha_i \circ \Omega \circ B^i \circ \Omega^{-1}.$$
% The result follows.
% \end{proof}

% \begin{remark}
% Lemma~\ref{lem:symp1} implies that when $\alpha_0$ is invertible all the relations in Equations~(\ref{eq:cons1})-(\ref{eq:cons2}) follow from the Equation~(\ref{eq:B^-1}) with $r=d_i-1$ and $r=d_i$.
% \end{remark}

%We unpack Equations~(\ref{eq1:cons2}) and (\ref{eq2:cons2}) to demonstrate that it is homogeneous with respect to the natural $G$ action on our fields:
%Precomposing $\wedge^{d_i+r} B_i$ by the inverse of isomorphism $I^{\dagger}_r(T_i \otimes V)$ and postcomposing $I^{\dagger}_r(\oplus T_j)$ gives a field that differs from $\alpha_i \circ B^i$ by some multiple of $L_V$.
%The factor $\alpha_0^r$ is used to fix this discrepancy.

% \begin{remark}
% With $r=d_i-1$, the relations in (\ref{eq1:cons2}) and (\ref{eq2:cons2}) come agonizingly close to expressing $B^i$ in terms of $B_{i}$ or vice versa but just miss because the fields $\alpha_i$ are not invertible.
% \end{remark}


% that the section $\wedge^{d_i} P_i$ maybe rewritten as $$\wedge^{d_i} P_i \colon \bigoplus_\lambda\, (\bS_\lambda T_i \otimes \bS_{\lambda'} V) \longrightarrow \bigoplus_{\sum_{i\rightarrow j} n_j=d_i} (\wedge^{n_j}T_j)$$
% where $\lambda$ is a partition of $d_i$ with $\lambda_1 \leq 2$ and $\lambda'$ being the partition dual to $\lambda$.
% Moreover, we have natural isomorphisms \begin{equation}
%     I_\lambda \colon \bS_\lambda \VW \rightarrow \bS_\lambda \VW^\vee \otimes L_W^2 \quad\quad \text{and} \quad\quad I^\dagger_k \colon \wedge^{k} \VW \rightarrow \wedge^{n-k} \VW^\vee \otimes L_W
% \end{equation}
% where $\VW$ is an $n$-dimensional vector space and $\lambda$ is a partition of $n$ for which $\lambda_1 \leq 2$.
% Precomposing $\wedge^{d_i} P_i$ by the respective $I_\lambda \otimes \text{id}_V$ and postcomposing with the appropriate direct sum of the isomorphisms $I_k^\dagger$ gives a section which is comparable to  $\alpha_i \circ (\wedge^{d_i} P_{i^\vee})$.

\subsection{The stack $\cN$}
This is the main character of the story.

\begin{definition}
The quotient stack $\cN$ is $\Y/\Gamma$.
Furthermore, for $\theta \in \bZ^{Q_0}$ a character of $\Gamma$, we write $\cN^\theta:= \Y^\theta/\Gamma$ where $\Y^\theta$ is the GIT $\theta$-semistable locus.
The standard representations $V_i$ of $\GL(V_i) \subset \Gamma$ give rise to universal bundles $\cV_i$ on $\cN$ while the linear maps $(\bfx, \balpha, \bfB)$ give corresponding universal sections.
\end{definition}

\begin{remark}
The stack $\cN$ may be thought of as the moduli space of functors from a monoidal category $\cC$ to the category of vector spaces.
This idea is pushed to a more general setting in subsequent work.
\end{remark}

Lemma~\ref{lem:rela} shows that a $\bC$-point of $\cN$ gives rise to one in $\cM$ via $(\bfx, \balpha, \bfB) \mapsto \widetilde{\bfB}(\bfx).$
This works in families too giving a morphism of stacks
\begin{align*}
    & f \colon \cN \longrightarrow \cM \\
    & (\bfx, \balpha, \bfB) \mapsto \widetilde{\bfB}(\bfx).
\end{align*}
This morphism features heavily in what follows.

We finish the section with a lemma that will be helpful when discussing the $\theta$-stability in relation to $f$.

\begin{lemma}\label{lem:Si}
If $\alpha_i=0$ then $S_i$ is a submodule of $\widetilde{\bfB}(\bfx)$.
\end{lemma}

\begin{proof}
If $\alpha_i=0$ then $\wedge^{d_i} B_i=0$ by Equation~\eqref{eq2:cons2}.
Therefore the $d_i$-th wedge of $$V_{i} \xrightarrow{\textup{id} \otimes \bfx} V_{i} \otimes \VW \xrightarrow{B_{i}} \bigoplus_{i \rightarrow j} V_j$$ is zero and this composite is not injective.
The kernel of this composite then gives a submodule of $\widetilde{\bfB}(\bfx)$ concentrated on the vertex $i$ and is therefore a direct sum of copies of $S_i$.
\end{proof}

% \begin{theorem}
% For a generic character $\phi \in \bZ^{Q_0}$ a point $(\bfx, \alpha_i, \bfB)$ is $\phi$-stable if and only if $\widetilde{\bfB}(\bfx)$ is $\phi^+$-polystable and $\alpha_i \neq 0$ for all $i \in I^\phi_-$.
% \end{theorem}

\section{Tannakian duality and the stack $\bX$}

The focus of this section is the open subset $$\cN^\circ:= \{\,(\bfx, \balpha, \bfB) \in \cN \,\,|\,\, \bfB \text{ is invertible} \,\}.$$
We show that it is isomorphic to $\bX$ and that $f \colon \cN^\circ \rightarrow \cM \rightarrow \cM^0=X$ is the coarse moduli space morphism.
We then go on to show that $\cN^\circ = \cN^{-\vartheta}$ for the generic stability parameter $-\vartheta$ so $\cN^{-\vartheta} \simeq \bX$.

\begin{remark}
The invertibility of $\bfB$ is equivalent to the invertibility of $\alpha_i$ for all $i \in I$; the determinant of $\bfB$, given by Equation~(\ref{eq:cons1}) with $r=d_i$, is a product of $\alpha_i$'s and has $\alpha_1 \cdots \alpha_N$ as a factor.
Also, when $\bfB$ is invertible Equation~(\ref{eq2:cons2}) allows us to express $\alpha_i$ in terms of $B_i$.
\end{remark}

Intertwiners $\beta_i^j \colon \rho_i \otimes_G \bC^2 \rightarrow \rho_j$ give a ring isomorphism $\bfe_0 \cA \bfe_0 \simeq \bC[x,y]^G$ and identify $\cM^0$ with $X$.
When $\bfB$ is invertible, we show that our linear maps $B_i^j \colon V_i \otimes \VW \rightarrow V_j$ do so too.
For a cycle $p$ of length $k$ with $t(p)=h(p)=0$ let $B_0^p$ denote the composite given by successive applications of $\bfB$ below $$V_0 \otimes \VW^{\otimes k} \longrightarrow \Bigg(\bigoplus_{i \rightarrow j} V_j\Bigg) \otimes \VW^{\otimes (k-1)} \rightarrow \cdots \rightarrow \bigoplus_{\text{paths } q \text{ length } k} V_{h(q)} \rightarrow V_{h(p)}=V_0.$$
Armed with a fixed isomorphism of vector spaces $\VW \simeq \bC^2$, the above allows us to define the following homomorphism of $\bC$-algebras:
\begin{align*}
\phi \colon \bfe_0 \cA \bfe_0 &\longrightarrow S(\VW^\vee) \simeq \bC[x,y]
\\ p &\mapsto (V_0 \otimes \VW^{\otimes k} \xrightarrow{B_0^p} V_0).
\end{align*}
Given $\bfx \in \VW$, \eqref{eq:Btilde} implies that the composite $$V_0 \xrightarrow{\bfx^k} V_0 \otimes \VW^{\otimes k} \xrightarrow{B_0^p} V_0$$ coincides with the linear map corresponding to $p$ in the representation $\widetilde{\bfB}(\bfx)$.
In other words, $\Spec(\phi)$ is the composite $\VW \xrightarrow{\widetilde{\bfB}} \cR \rightarrow \cM^0$.

\begin{lemma}\label{lem:e0Ae0}
When $\bfB$ is an isomorphism, the homomorphism $\phi \colon \bfe_0 \cA \bfe_0 \rightarrow \bC[x,y]$
induces an isomorphism between the image of $\phi$ and $\bC[x,y]^G$.
Equivalently, the morphism $$\bC^2 \simeq \VW \xrightarrow{\widetilde{\bfB}} \cR \rightarrow \cM^0 \simeq X$$ is the quotient morphism $\pi$ up to an automorphism of $X$.
\end{lemma}

\begin{proof}
Let $\psi \colon \bfe_0 \cA \bfe_0 \longrightarrow \bC[x,y]^G$ be the isomorphism given by the intertwiners $\rho_i \otimes_G \bC^2 \rightarrow \rho_j$.
This gives us a ring homomorphism $\phi \circ \psi^{-1} \colon \bC[x,y]^G \rightarrow \text{im}(\phi)$.
This composite homomorphism is an isomorphism of vector spaces and so it is a ring isomorphism.
\end{proof}

\begin{theorem}\label{thm:tannaka}
The stack ${\cN}^\circ$ is isomorphic to $\bX$.
%Moreover $f \colon {\cN}^\circ \rightarrow \cM^0 = X$ is the coarse moduli space.
\end{theorem}

\begin{proof}
Let $\Hom(\VW, \cR)$ denote the subvariety of the affine space $$\Bigg(\bigoplus_{0\neq i \in Q_0} \Hom\Big(L_i \otimes L_i,\, \bigotimes_{i \rightarrow j} L_j\Big) \Bigg) \oplus \Hom(\VW,\cS)$$ whose points satisfy the relations given in Equations~(\ref{eq:cons1})-(\ref{eq:cons2}) and for which the the corresponding $\bfB$ is an isomorphism.
Elements of $\Hom(\VW, \cR)$ are determined by the $\Hom(\VW,\cS)$ summand since the scalars $\alpha_i$ may be deduced from the relations in this case; we will be denoted them by $\widetilde{\bfB}$ as before.
We consider the stack $[\Hom(\VW,\cR)/\Gamma]$.

We show that the change of basis action of $\Gamma$ on $\Hom(\VW,\cR)$ is transitive, i.e.\  for $\bfB, \bfB' \in \Hom(\VW,\cR)$ there exists $\gamma \in \Gamma$ such that $\bfB = \gamma \cdot \bfB'$.
Lemma~\ref{lem:e0Ae0} above allows us to assume that the composites  
$$\bC^2 \simeq \VW \rightarrow \cR \rightarrow \cR \GIT \Gamma = \Spec(\bfe_0 \cA \bfe_0) = X$$
corresponding to $\bfB$ and $\bfB'$ are both the quotient morphism $\pi$.
Let $\cR' \subset \cR$ be the inverse image of $(\VW \setminus 0) / G$ under  $\cR \rightarrow \cR \GIT \Gamma = X$ and note that $\Gamma$ acts freely on $\cR'$ with $\cR' / \Gamma = (\VW \setminus 0) / G$.
Our assumption then implies that $\widetilde{\bfB}$ and $\widetilde{\bfB}'$ give rise to the same morphism $\VW \rightarrow \cR'/\Gamma$ and so we have a morphism $\VW \rightarrow \cR' \times \Gamma$.
This morphism factors to through $(\id, \gamma) \colon \cR' \rightarrow \cR' \times \Gamma$ for some $\gamma \in \Gamma$ because both $\widetilde{\bfB} \colon \VW \rightarrow \cR \rightarrow \cS$ and $\widetilde{\bfB}' \colon \VW \rightarrow \cR \rightarrow \cS$ are linear maps.
That is, $\bfB = \gamma \cdot \bfB'$.

To determine the stabilizer of this action, take $\bfB$ defined by the intertwiners $\beta_i^j$.
The standard statement of Tannakian duality for finite groups translates to the stabilizer of $\bfB$ being precisely $G \in \Gamma$.

The above shows that $[\Hom(\VW,\cR)/\Gamma]$ is isomorphic to the classifying stack $BG$.
Adding $\bfx \colon V_0 \rightarrow \VW$ to the data then gives the result.
% of sections $\bfB$ up to the action of $\Gamma$ give the stack $BG$.
% Given $\bfB$, we study the associated $\widetilde{\bfB}$.
% We will show that the quotient of $\{\widetilde{\bfB}\} /\Gamma$ is isomorphic to $\{\pi \colon \VW \rightarrow \VW\GIT G\}/\GL(\VW)$ with $\GL(\VW)$ acting on the domain.
% Given $\widetilde{\bfB}$, taking invariants gives 
% $$\VW \xrightarrow{\widetilde{\bfB}} \cR \rightarrow \cR \GIT \Gamma = \Spec(\bfe_0 \cA \bfe_0) = \VW\GIT G.$$
% Since our point is in $\cN^\circ$ the section $\bfB$ is invertible; Lemma~\ref{lem:e0Ae0} gives the composite is $\pi$ up to an automorphism of $\VW//G$.
% Every such automorphism maybe lifted to one of $\VW$ so, up to the action of $\GL(\VW)$ on the domain, this is $\pi$.
% The projection $\Gamma \rightarrow \GL(\VW)$ makes this morphism equivariant.
% Taking $\pi$ to the $\bfB$ defined by the intertwiners defines an inverse that is equivariant with respect to the inclusion $\GL(\VW) \rightarrow \Gamma$.
% % Two points $\bfx, \bfy \in \VW$ lie in the same $G$-orbit if and only if $p(\bfx)=p(\bfy)$ for every $p \in S(\VW^\vee)^G$.
% % For $p \in S^k(\VW^\vee)^G$, we may interpret $p(\bfx)$ as the linear maps $$\bC = V_0 \xrightarrow{\bfx^{\otimes k}} V_0 \otimes \VW^{\otimes k} \xrightarrow{p} V_0=\bC$$ and similarly for $p(\bfy)$.
% % On the other hand, via $S^k(\VW^\vee)^G \simeq \bfe_0 \cA \bfe_0$, the element $p$ specifies a linear combination of cycles centred at 0 of length $k$.
% % Let $\bfB^k$ denote the composite given by successive application of $\bfB$ below $$V_0 \otimes \VW^{\otimes k} \longrightarrow \Bigg(\bigoplus_{i \rightarrow j} V_j\Bigg) \otimes \VW^{\otimes (k-1)} \rightarrow \cdots \rightarrow \bigoplus_{\text{paths } q \text{ length } k} V_{h(q)}.$$
% % Since $\bfB$ is an isomorphism so is $\bfB^k$.
% % By Lemma~\ref{lem:Btilde}, the linear map corresponding to this linear combination in $\widetilde{\bfB}(\bfx)$ is $$V_0 \xrightarrow{\text{id} \otimes \bfx^{\otimes k}} V_0 \otimes \VW^{\otimes k} \xrightarrow{\bfB^k} \bigoplus_{\text{paths } q \text{ length } k} V_{h(q)} \xrightarrow{p} V_0$$
% % respectively.
% %The claim follows because $\bfB^k$ is an isomorphism.
% Since $\VW\setminus \{0\}$ is a $G$-torsor we have that $\{\pi \colon \VW \rightarrow \VW\GIT G\}/\GL(\VW) \simeq BG$ and hence so is $\{\widetilde{\bfB}\} /\Gamma$.
% The data of $\balpha$ is accounted for since we are restricted to the subset where $\bfB$ is an isomorphism.
% Adding $\bfx \colon V_0 \rightarrow \VW$ to the data then gives the result.
\end{proof}

% \begin{proof}
% We unfortunately do this case by case.
% The overriding idea is to start with the representation at the `special' vertex $T_0$ of the McKay quiver and reduce the $P_i$s to a normal form one by one from there.
% The first representation one meets from $T_0$ is $V$ and the next one down is a summand of $V \otimes V$ and so on, therefore in tensor categorical terms this strategy goes through understanding the fusion graph of the faithful representation $V$.

% The $A_n$ case is easy, everything in sight is rank 1 or direct sums of rank 1s.

% For $D_n$, we have that $V=T_2$.
% We pick a bases $\{e_1,e_2\}$ for $T_2$ to help with expressing what follows.
% We take the monomials of degree $n$ with respect to this basis as a basis for $S^n(T_2)$.
% Up to the fixed isomorphism $\bfk \simeq T_0$, we may take $P_0$ is taken to be the identity.
% The section $P_{0^\vee}$ naturally gives a map $P_2^0 \colon T_2 \otimes V \rightarrow T_0$, the constraint (\ref{eq1:cons2}) with $i=0$ and $r=0$ then implies that this factors through $L_V=L_2$.
% A choice of $P_{0^\vee}$ fixes a coset of $\SL(T_2)$ in $\GL(T_2)$.

% We next consider the field $P_2$, semi-simplicity implies that $P_2^1$ is orthogonal to $P_2^0$ and so factors through $S^2(T_2)$.
% The constraint (\ref{eq1:cons2}) with $i=1$ and $r=0$ gives us $P_{1^\vee}$ and hence $P_1$.
% The condition that $P_2^1$ factors through $S^2(T_2)$ then translates into into tracelessness of $P_1$.
% We may then act by $SL(T_2)$ by conjugation on $P_1$ to bring it to the form $\text{diag}(\lambda,-\lambda)$ for $\lambda \in \bfk^\times$.
% %Scaling by $T_1$ we take $\lambda$ so that $\lambda^2=-1$.
% Translating back to $P_2^1$ via the constraints, we get that $P_2^1 \colon S^2(T_2) \rightarrow T_1$ factors through the subspace generated by $e_1 e_2$.
% Semi-simplicity then implies that $P_2^3 \colon S^2(T_2) \rightarrow T_3$ is orthogonal to $P_2^1$ and so factors through the subspace $\{e_1^{\otimes 2}, e_2^{\otimes 2}\}$.
% %We may act on $S^2(T_2) \rightarrow T_3$ by $\GL(T_3)$ to fix $\mu_1=1$ and $\mu_2=1$.

% The constraint (\ref{eq1:cons2}) with $i=2$ and $r=1$ gives $P_{2^\vee}$ up to scalar.
% From this, using some natural identities, we may deduce $P_3^2$ up to a scalar multiple.
% Semi-simplicity then specifies the 2-dimensional subspace of $\Hom(T_3 \otimes T_2, T_4)$ in which the field $P_3^4 \colon T_3 \otimes T_2 \rightarrow T_4$ lives.
% A careful consideration of this subspace gives that $$T_2 \otimes S^2(T_2) \xrightarrow{\text{id} \otimes P_2^3} T_2 \otimes T_3 \xrightarrow{P_3^4} T_4$$ must factor through $S^3(T_2)$ and in particular, for our choices above, through the subspace generated by the tensors $e_1^{\otimes 3}$ and $e_2^{\otimes 3}$.
% We may act on $P_3^4$ by $\GL(T_4)$ to bring it to any form we like.

% We proceed to argue like so all the way up to the last rank two representation $T_{n-2}$ reducing all $P_i$ for $i\leq (n-3)$ to some normal form.
% This in turn, by the constraints, fixes $P_{n-2}^{n-3}$ up to scalar.
% We leave $T_{n-2}$ for now and focus on the rank 1 representations $T_{n-1}$ and $T_n$.
% We fix isomorphisms $P_{n-1}$ and $P_n$ so that the corresponding $P_{n-2}^{n-1}$ and $P_{n-2}^{n}$ are mutually orthogonal and orthogonal to $P_{n-2}^{n-3}$; this is designed to satisfy the semi-simplicity constraint.
% Again examining the subspace in which $P_{n-2}^{n-3}$ lives we may deduce that this orthogonality implies that $$T_2 \otimes S^{(n-3)}(T_2) \xrightarrow{\text{id} \otimes P_{n-3}^{n-2}} T_2 \otimes T_{n-2} \xrightarrow{P_{n-2}^{n-1}} T_{n-1}$$
% factors through the subspace of $S^{(n-2)}(T_2)$ generated by $e_1^{\otimes (n-2)}$ and $e_2^{\otimes (n-2)}$.

% Now we may act by $\SL(T_2)$ to transform $P_{n-1}$ into a form we like while preserving everything else.

% \end{proof}

\begin{corollary}
The stack $\cN^{-\vartheta}$ is isomorphic to $\bX$.
\end{corollary}

\begin{proof}
We show that $\alpha_i \neq 0$ for all $i \in I$ is equivalent to $(-\vartheta)$-stability.

Take $(\bfx, \balpha, \bfB) \in \cN^{-\vartheta}$. 
Assume, seeking a contradiction, that $\alpha_i =0$ for some $i \in I$ then by Lemma~\ref{lem:Si} we have that $S_i$ is a subrepresentation of $\widetilde{\bfB}(\bfy)$ for any $\bfy \in \VW$.
Let $\lambda \in \Gamma$ be the one-parameter subgroup corresponding to $S_i$.
The above then implies that the limit $t \rightarrow 0$ of $\lambda \cdot \widetilde{\bfB}$ exist.
The limit also exists for $\bfx$ since $\lambda$ acts with positive powers on $\bfx$.
The subgroup $\lambda$ acts with positive powers on $\alpha_j$ for all $i\neq j\in I$ and so the corresponding limits exists too.
It remains to check $\alpha_i$ but $\alpha_i=0$ so the desired limit exists there.
We may therefore apply the Hilbert-Mumford criterion with the one-parameter subgroup $\lambda$.
The pairing $\langle \lambda, -\vartheta \rangle$ is negative and hence $(\bfx, \balpha, \bfB)$ is $(-\vartheta)$-unstable yielding our desired contradiction.

The fact that entries of the inverse of the Cartan matrix are non-negative rational numbers implies that a product of fields $\alpha_i$ gives a non-zero semi-invariant of weight $n\cdot (-\vartheta)$ for some positive $n \in \bN$.
% {\red This is a white lie:}
% For $(\bfx, \balpha, \bfB) \in \cN^\circ$, the section $\alpha_0$ is a non-zero semi-invariant of weight $-\vartheta$.
% Therefore $(\bfx, \balpha, \bfB)$ is $(-\vartheta)$-stable.
% Equation~\ref{eq1:cons2} expresses the determinant of $B_i$, and hence $\bfB$, in terms of the scalars $\alpha_i$.
% Furthermore, we have that the weight of $\bfx \colon V_0 \rightarrow \VW$ is opposite to that of $\alpha_0 \colon L_W \rightarrow L_0$ and so setting $\bfx=0$ does not alter the $\phi$-stability of a point $(\bfx, \alpha_i, \bfB)$.
% Therefore the determinant of any semi-invariants with weight $n \phi$, for $n>0$, must contain the scalar field $\otimes_{i\in I} \, \alpha_i$ as a factor.
% Therefore $\otimes_{i\in I} \, \alpha_i \neq 0$ for any $\phi$-stable point of $\cM$ which implies that $\alpha_i$s are are invertible and hence also $\bfB$.
% The corollary may also be be deduced from Lemma~\ref{lem:Si}.
\end{proof}

\begin{remark}
For a point $(\bfx, \balpha, \bfB) \in \cN^\circ$, Lemma~\ref{lem:e0Ae0} and Theorem~\ref{thm:tannaka} show that the data in $\bfB$ is equivalent to that of a monoidal fibre functor $\Rep(G) \rightarrow \Vect$ and hence the name of the section.
\end{remark}

\section{The $G$-Hilbert Scheme}
In this section we show that the restriction of $f \colon \cN \rightarrow \cM$ to $\cN^\vartheta$ factors through $\cM^\vartheta$.
We go on to construct an inverse $g \colon \cM^\vartheta \rightarrow \cN^\vartheta$ to this restriction of $f$ showing it is an isomorphism.
This then proves that $\cN^\vartheta \simeq G\text{-Hilb}(\VW)$.

% Let $\cN^\theta$ denote the quotient of $\theta$-stable fields up to the constraints and $\Gamma$-action.
% We construct morphisms $f \colon \cN^\theta \rightarrow \cM^\theta$ and $g \colon \cM^\theta \rightarrow \cN^\theta$ and show that they are mutual inverses.

\begin{proposition}
The morphism $f \colon \cN \rightarrow \cM$ restricted to $\cN^\vartheta$ factors through $\cM^\vartheta$.
\end{proposition}

\begin{proof}
For $(\bfx, \balpha, \bfB) \in \cN^\vartheta$, we show that $S_i$ can not be a quotient of $\widetilde{\bfB}(\bfx)$. This implies $\vartheta$-stability since any destabilizing quotient of $\widetilde{\bfB}(\bfx)$ is an extension of vertex simples $S_i$.
Assume seeking a contradiction that $S_i$ is a quotient of $\widetilde{\bfB}(\bfx)$.
This is equivalent to the vanishing of the $d_i$-th wedge of the linear map
$$\bigoplus_{i \rightarrow j} V_j \xrightarrow{B^i} V_i \otimes \VW^\vee \xrightarrow{\text{id} \otimes \bfx^T} V_i.$$

Equation~(\ref{eq2:cons2}) then implies that $S_i$ also a submodule of $\widetilde{\bfB}(\bfx)$ since the $d_i$-th wedge of 
$$V_i \xrightarrow{\text{id} \otimes \bfx} V_i \otimes \VW \xrightarrow{B_i} \bigoplus_{i \rightarrow j} V_j$$
vanishes too.
In fact, the commutative diagram (\ref{eq:comdiag}) implies that $S_i$ is a direct summand of $\widetilde{\bfB}(\bfx)$.
Therefore evaluating 
\begin{equation}\label{eq:limB}
\VW \xrightarrow{\widetilde{\bfB}} \cR \longrightarrow \Big(\bigoplus_{i \rightarrow j} \Hom(S_i,V_j) \oplus \bigoplus_{j \rightarrow i} \Hom(V_j, S_i)\Big)
\end{equation}
on $\bfx$ yields 0.
Since, by an argument similar to Lemma~\ref{lem:symp2}, the composite above is symplectic and $\dim \VW=2$ this is zero on all of $\VW$.

The quotient $S_i$ of $\widetilde{\bfB}(\bfx)$ by King's argument corresponds to a 1-parameter subgroup $\lambda$ of $\Gamma$ that is the identity on the summands $\GL(V_j)$ for all $j\neq i$ and has negative weight on $\GL(V_i)$. 
Now $\langle \lambda, \vartheta\rangle <0$, therefore $\lambda$ would destabilise $(\bfx, \balpha, \bfB)$ if $\lim_{t \rightarrow 0} \, \lambda(t)\cdot (\bfx, \balpha, \bfB)$ was to exist.
The summand $\GL(V_i)$ acts on $\bfx$, $\alpha_i$ and $\alpha_k$ for $k \in Q_0$ not adjacent to $i$ with non-positive weight and so the corresponding limits exist for $\lambda$.
The vanishing of the linear map in (\ref{eq:limB}) implies that $\lim_{t \rightarrow 0}\, \lambda(t)\cdot \widetilde{\bfB}$ exists.
To reach our desired contradiction, it remains to show that the limit exists for $j$ adjacent to $i$; this is the case only when $\alpha_j=0$.

Assume $\alpha_j \neq 0$.
We have that the following sequence is not exact since $i$ is adjacent to $j$ and $S_i$ is a summand of $\widetilde{\bfB}(\bfx)$
$$0 \longrightarrow V_j \longrightarrow \bigoplus_{j \rightarrow k} V_k \longrightarrow V_j \longrightarrow 0.$$
Equation~\eqref{eq2:cons2} and $\alpha_j \neq 0$ means that it is not exact on either side: if it is not exact on the left it is not on the right and vice versa.
Therefore $S_j$ is also a quotient in $\widetilde{\bfB}(\bfx)$.
We leave it for the reader to check that this is compatible with $S_i$, that is that the argument implies that $S_i \oplus S_j$ is a summand of $\widetilde{\bfB}(\bfx)$.
The 1-parameter subgroup corresponding to $S_i \oplus S_j$ then either has a limit and is destabilising or $S_i \oplus S_j$ is extendable to a bigger summand as above.
\end{proof}

\subsection{The inverse morphism}

We define a morphism  $g \colon \cM^\vartheta \rightarrow [\bA/\Gamma]$.
We show that $g$ factors through $\cN^\vartheta$ and is hence a candidate for the inverse of $f \colon \cN^\vartheta \rightarrow \cM^\vartheta$.
We then go on to prove that it indeed is $f^{-1}$.

Take $(\cV_i, v_a)$ to be the universal family on $\cM^\vartheta$.
To define $g$ it suffices to describe the pullback of the universal sections $\bfx$, $\balpha$ and $\bfB$ on the vector bundles $\cV_i$.

\subsubsection{The field \bfx}

The representation $\VW$ either corresponds to a single vertex if irreducible or a pair of vertices if not.
The arrows from vertex $0$ to vertices corresponding to $\VW$ gives us a tautological section $\cV_0 \rightarrow \cW$ we take that to be the $\bfx$ of Equation~(\ref{fd:x}).

\subsubsection{The field $\balpha$}\label{sssc:alpha}

Take $0 \neq i \in Q_0$.
Since our family is $\vartheta$-stable and $\vartheta_i>0$, the universal section corresponding to arrows whose heads are $i$ is surjective, i.e.\ the following is exact:
\begin{equation}\label{eq:k}
    \bigoplus_{i \rightarrow j} \cV_j \longrightarrow \cV_i \longrightarrow 0.
\end{equation}
Take $\c\Y$ to be its kernel.
The relation $r_i \in R$ give us a complex
$$\cV_i \longrightarrow \bigoplus_{i \rightarrow j} \cV_j \longrightarrow \cV_i \longrightarrow 0$$
and hence a morphism $\cV_i \rightarrow \c\Y$.
We take $\alpha_i$ to be $\wedge^{d_i} \cV_i \rightarrow \wedge^{d_i}\c\Y.$

\subsubsection{The field $\bfB$}
In this construction, will use the isomorphism $\End_{\cM^\theta}(\oplus_i V_i) \simeq \End^{\text{op}}_\cA(\oplus_i P_i)$.
We have that the isomorphism of $G$-representations $\rho_i \otimes \VW \rightarrow \oplus_j\, \rho_j$ induces a morphism of $G$-representations $$\underline{\Hom}_G(\VW,\rho_0) \longrightarrow \underline{\Hom}_G(\oplus_j \, \rho_j, \rho_i).$$
This, in turn, gives a linear map of Hom-spaces of the corresponding projective modules $P_i$ and a suggestively named linear map $H^0(\widetilde{\bfB})$:
\begin{equation}\label{eq:homsp}
    H^0(\widetilde{\bfB}) \colon {\Hom}(\cV_0, \cW) \longrightarrow {\Hom}(\cV_i, \oplus_j \, \cV_j).
\end{equation}

Next we use $\vartheta$-stability of the universal family $(\cV_i, v_a)$.
We have that $\vartheta_0<0$ and $\vartheta_i>0$ for all other $i$ therefore the evaluation morphism $$\text{ev} \colon \cV_0 \otimes_\bC {\Hom}(\cV_0, \cW) \longrightarrow \cW$$ is surjective.
Combining this with Equation~(\ref{eq:homsp}) above we get a composite
$$\cV_0 \otimes_\bC {\Hom}(\cV_0, \cW) \longrightarrow \cV_0 \otimes_\bC {\Hom}(\cV_i, \oplus_j \, \cV_j) \longrightarrow\ \cV_i^\vee \otimes \Big(\bigoplus_{i \rightarrow j}\cV_j\Big)$$
where the second factor is also an evaluation map.
We claim that the kernel of ev is zero under this composite which yields a section 
$$\widetilde{B}_i \colon \cW \longrightarrow \cV_i^\vee \otimes \Big(\bigoplus_{i \rightarrow j}\cV_j\Big).$$
Summing over the vertices $i$ gives us $\widetilde{\bfB}$ and hence $\bfB$.
It remains to prove the claim.

\begin{proof}[Proof of claim]
Take $\cK$ in the kernel of $\ev$.
We may assume that this is a universal bundle since universal bundles generate $D^b(\cM^\vartheta)$ so take $\cK=\cV_k$.

We now translate the statement in terms of Hom-spaces of the corresponding projective modules and use the monoidal structure induced by $G$-representations there.
The fact that $\cK$ is in the kernel is given by an element $p$ in the kernel of 
\begin{equation}
    \Hom(P_k, P_0) \otimes_\bC \Hom(P_0, P_{\VW}) \longrightarrow \Hom(P_k, P_{\VW}).
\end{equation}
That is, $p$ corresponds to a linear combination of paths from $k$ to $0$ and a linear combination of paths from $0$ to $\VW$ for which the product is in the ideal of relations.
The following diagram is commutative:
\begin{equation*}
    \xymatrix{\Hom(P_k, P_0) \otimes_\bC \Hom(P_0, P_{\VW}) \ar[r] \ar[d]^{- \otimes_G P_i} & \Hom(P_k, P_{\VW}) \ar[d]^{- \otimes_G P_i} \\
    \Hom(P_k \otimes_G P_i, P_i) \otimes_\bC \Hom(P_i, P_\cW \otimes_G P_i) \ar[r] & \Hom(P_k \otimes_G P_i, P_\cW \otimes_G P_i).}
\end{equation*}
The module $P_\cW \otimes_G P_i$ is $\oplus_j P_j$, similarly $P_k \otimes_G P_i$ is isomorphic to a projective module $P_l$. 
Mapping $p$ through the vertical linear map $- \otimes_G P_i$ gives an element of $\Hom(P_l, P_i) \otimes_\bC \Hom(P_i, \oplus_j P_j)$.
The commutativity of the diagram implies that this gives rise to an element of the kernel of the evaluation map $$\cV_i \otimes_\bC \Hom(\cV_i, \oplus_j \cV_j) \rightarrow \oplus_j \cV_j$$
Adjunction completes the proof.
\end{proof}

% \begin{remark}
% The kernel $\fK$ is quasi isomorphic to the complex in (\ref{eq:k}).
% As with any Schur functor, the top wedge of a complex maybe expressed as a complex.
% We may equivalently use this expressing of the top wedge along with the constraints (\ref{eq1:cons2}) and (\ref{eq2:cons2}) to define $\alpha_i$.
% \end{remark}

\subsubsection{The relations and conclusion}

The above construction defines a morphism $g \colon \cM^\vartheta \rightarrow [\bA/\Gamma]$ here we show that it in fact factors through $\cN^\vartheta$.
Then prove it is $f^{-1}$.

Theorem~\ref{thm:tannaka} gives that $\cM^\vartheta$ and $\cN^\vartheta$ are birational via $f \colon \cN \rightarrow \cM$.
To deduce that the relations are satisfied we first show that $f \circ g \colon \cM^\vartheta \rightarrow \cM^\vartheta$ is the identity on the open subset of points of $\cM^\vartheta$ corresponding to free orbits of the $G$-action on $\VW$.

\begin{theorem}\label{thm:fg}
The morphism $f \circ g \colon \cM^{\vartheta} \longrightarrow \cM$ factors through $\cM^\vartheta$ and is the identity on it.
\end{theorem}

\begin{proof}
Take $\bfe_\bfx \colon \cV_0 \rightarrow \cV_0 \otimes_\bC \Hom(\cV_0, \cW)$ to be the section taking $\cV_0$ to the component corresponding to the arrow(s) with tail at the vertex $0$.
The right hand column of the following diagram is how $f$ is defined while the left hand column is how $g$ is defined.
\begin{equation}\label{eq:gf}
    \xymatrix{\cV_0 \ar[r]^{\text{id}} \ar[d]^{\bfe_\bfx} & \cV_0 \ar[d]^\bfx \\
    \cV_0 \otimes_\bC \Hom(\cV_0, \cW) \ar[r]^-{\text{ev}} \ar[d]^{\text{id} \otimes H^0({\widetilde{\bfB}})} & \cW \ar[d]^{\widetilde{\bfB}} \\
    \cV_0 \otimes_\bC \Hom(\cV_i, \oplus_j \cV_j) \ar[r]^-{\text{ev}} & \cV_i^\vee \otimes \Big(\bigoplus_{i \rightarrow j}\cV_j\Big).
    }
\end{equation}
The commutativity of the diagram then gives the result.
\end{proof}

\begin{corollary}
The morphism $g \colon \cM^\vartheta \rightarrow [\bA/\Gamma]$ factors through the closed subset $\cN \subset [\bA/\Gamma]$.
\end{corollary}

\begin{proof}
Theorem~\ref{thm:fg} gives that $g$ is a left inverse to the birational map $f$; it is therefore a two-sided inverse.
The restriction of $g$ to a dense open subset of $\cM^\vartheta$ factors through the closed subset $\cN \subset [\cA/\Gamma]$ which implies unrestricted morphism $g$ does too.
\end{proof}

\begin{corollary}
The morphism $g \colon \cM^\vartheta \longrightarrow \cN$ factors through the open subset $\cN^\vartheta$.
\end{corollary}

\begin{proof}
The $\vartheta$-stability of a point in $\cM^\vartheta$ is guaranteed by the non-vanishing of section of a power of $\otimes_{i \in Q_0} L_i$.
We may construct such a section on a point $(\bfx, \balpha, \bfB)$ in the image by taking the corresponding section on $\widetilde{\bfB}(\bfx)$.
This section remains non-zero by Theorem~\ref{thm:fg}.
\end{proof}

We now have a morphism $g \colon \cM^\vartheta \rightarrow \cN^\vartheta$ and so a candidate for the inverse of $f$.

\begin{theorem}\label{thm:ghilb}
The morphism $g \circ f \colon \cN^\vartheta \rightarrow \cN^\vartheta$ is the identity.
\end{theorem}

\begin{proof}
%Theorem~\ref{thm:fg} gives that $f \circ g$ is the identity, it remains to show that $g \circ f \colon \cN^\vartheta \rightarrow \cN^\vartheta$ is too.
Take $\cV_i$ with sections $(\bfx, \balpha, \bfB)$ to be the universal family on $\cN^\vartheta$.
The vector bundles remain unchanged by $g \circ f$ and so does the section $\bfx$.
The proof of Theorem~\ref{thm:fg}, in particular the bottom half of the commutative diagram (\ref{eq:gf}), shows that the same is true for $\bfB$.

We now focus on the sections $\alpha_i$.
The $d_i$-th wedge of the complex
$$\bigoplus_{j \rightarrow i} \cV_j \xrightarrow{(B^i \,\circ\, \bfx)^T} \cV_i$$
is the complex
\begin{equation}\label{eq:dthwedge}
    \bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg) \rightarrow \bigwedge^{d_i-1} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg) \otimes \cV_i \rightarrow \cdots \rightarrow S^{d_i}(\cV_i).
\end{equation}
In Section~\ref{sssc:alpha} the section $\alpha_i$ on points in the image of $g$ is defined as the $d_i$-th wedge of the morphism of complexes
\begin{equation*}
    \xymatrix{\cV_i \ar[rr] \ar[d]^{B_i \,\circ\, \bfx} && 0 \ar[d] \\
    \bigoplus_{j \rightarrow i} \cV_j \ar[rr]^-{(B^i \,\circ\, \bfx)^T} && \cV_i.}
\end{equation*}
That is, $\alpha_i$ is given by the composite 
\begin{equation}\label{eq:alpha}
    L_i \xrightarrow{\bfx^{d_i}} L_i \otimes S^{d_i}(\cW) \xrightarrow{\wedge^{d_i} B_{i}} 
%\bigotimes_{i \rightarrow j} L_j  \otimes \bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg) = 
\bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg).
\end{equation}

By Equation~\eqref{eq2:cons2} we may rewrite (\ref{eq:alpha}) as 
$$L_i \xrightarrow{\alpha_i} \bigotimes_{i \rightarrow j} L_j  \otimes L_i^\vee \xrightarrow{\bfx^{d_i}} \bigotimes_{i \rightarrow j} L_j \otimes L_i^\vee \otimes S^{d_i}(\cW) \xrightarrow{\Omega \,\circ\, (\wedge^{d_i} B^i) \,\circ\, \Omega} 
%\bigotimes_{i \rightarrow j} L_j  \otimes \bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg) = 
\bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg)$$
Now our family $(\bfx, \balpha, \bfB)$ is $\vartheta$-stable therefore the section $(B^i \circ \bfx)^T$ is surjective and the composite $$\bigotimes_{i \rightarrow j} L_j  \otimes L_i^\vee \xrightarrow{\bfx^{d_i}} \bigotimes_{i \rightarrow j} L_j \otimes L_i^\vee \otimes S^{d_i}(\cW) \xrightarrow{\Omega \,\circ\, (\wedge^{d_i} B^i) \,\circ\, \Omega} 
%\bigotimes_{i \rightarrow j} L_j  \otimes \bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg) = 
\bigwedge^{d_i} \Bigg(\bigoplus_{j \rightarrow i} \cV_j \Bigg)$$
gives an isomorphism of $\bigotimes_{i \rightarrow j} L_j  \otimes L_i^\vee$ with the complex in (\ref{eq:dthwedge}).
This completes the proof.
\end{proof}

\begin{corollary}
The morphism $f \colon \cN^\vartheta \rightarrow \cM^\vartheta$ is an isomorphism.
In particular, $\cN^\vartheta \simeq G\textup{-Hilb}(\VW)$.
\end{corollary}

\section{Examples}

% This section will serve both as a demonstration that the above GIT problem maybe expressed as an affine space (linear) modulo the action of a reductive group and as an examples section.
% That is, we will demonstrate this case-by-case.
% The idea is that $\bfB$ gives a symplectic matrix when invertible.
% Up to scalars, the manifold of symplectic matrices maybe thought of as a flag variety which is an affine spaces modulo the action of a reductive group.

% Fix a vertex $i \in Q_0$ and consider the linear map $B_i \oplus B^i$.
% The relations imply that this a symplecto-morphism.
% In particular, given a choice of bases the rows of $B_i$ are orthogonal with respect to the symplectic forms in question.
% They are therefore given by a complete flag.

\subsection{Type $A$}
Here we have $G=\bZ/n\bZ=\langle 1\rangle$ and the representation $\VW$ is
\begin{align*}
    \VW \colon \, \bZ/n\bZ &\longrightarrow \SL(2,\bC) \\
    1 &\mapsto \begin{pmatrix} \varepsilon & 0 \\ 0 & \varepsilon^{n-1} \end{pmatrix}
\end{align*}
where $\varepsilon$ is a primitive $n$-th root of unity.
Take $\rho_i$ to be the rank one representation taking $1$ to $\varepsilon^i$, so that $\VW=\rho_1 \oplus \rho_{n-1}$.
We also have that $\rho_i \otimes \VW \simeq \rho_{i-1} \oplus \rho_{i+1}$.

Since $G$ is abelian and all irreducible representations are of rank 1, we have that $V_i = L_i$ so we write $$\alpha_i \colon V_i \otimes V_i \longrightarrow V_{i-1} \otimes V_{i+1}.$$
The sections $B_i$ are of the form $$B_i \colon V_i \otimes \VW \longrightarrow V_{i-1} \oplus V_{i+1}.$$

We have that $B_0 = \text{id}$.
The commutative diagram (\ref{eq:comdiag}) applied to $B_0$ then gives an expression for $B^0$.
In particular, we have that 
$$B_1^0 \colon (V_1 \otimes V_1) \oplus (V_1 \otimes V_{n-1}) \xrightarrow{(0\,\, \alpha_0)} V_0.$$
We now tackle $B_1$, so far we have 
\begin{align*}
    B_1 &\colon (V_1 \otimes V_1) \oplus (V_1 \otimes V_{n-1}) \xrightarrow{\begin{pmatrix} - & - \\ 0 & \alpha_0 \end{pmatrix}} V_2 \oplus V_0 \\
    B^1 &\colon (V_1^\vee \otimes V_1^\vee) \oplus (V_1^\vee \otimes V_{n-1}^\vee) \xrightarrow{\begin{pmatrix} 1 & 0 \\ - & - \end{pmatrix}} (V_0^\vee \oplus V_2^\vee) \otimes V_1^\vee \otimes V_{n-1}^\vee.
\end{align*}
We also have that
$$\alpha_1 \circ \Omega \circ B^1 \circ \Omega \colon (V_1 \otimes V_1) \oplus (V_1 \otimes V_{n-1}) \xrightarrow{\begin{pmatrix} \alpha_1 & 0 \\ - & - \end{pmatrix}} V_2 \oplus V_0.$$
Equation~(\ref{eq2:cons2}) completes the description of $B_1$.
A similar technique gives $B_2$; we may continue in this fashion to deduce 
$$B_i \colon (V_i \otimes V_1) \oplus (V_i \otimes V_{n-1}) \xrightarrow{\begin{pmatrix} \alpha_1\cdots\alpha_i & 0 \\ 0 & \alpha_{i+1}\cdots\alpha_{n-1} \end{pmatrix}} V_{i+1} \oplus V_{i-1}.$$

Since the sections $B_i$ are all diagonal matrices with diagonal entries made up of the sections $\alpha_i$ they are superfluous in type $A$.
We are then left with the space sections $\bfx$ and $\balpha$ up to the action of $\Gamma$ which in this case is a torus.
In type $A$, the variety $G$-Hilb$(\VW)$ is toric and this quotient construction coincides with that of Cox which achieves the goals of this construction in this work.

\subsection{Type $D_4$}
We examine the first non-trivial case, that of type $D_4$, in more detail.
The group in questions is:
$$G= \left\langle \,\sigma=\begin{pmatrix} e^{\pi/2} & 0 \\ 0 & e^{-\pi/2} \end{pmatrix},\,\, \tau=\begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix} \,\right\rangle \subset \SL(2, \bC).$$
The definition of $G$ above gives us the representation $\VW$. The representation $\VW$ is $V_2$ with $D_4$ labelled as below:
\begin{equation*}
    \dynkin[extended,Coxeter,label,scale=1.75]D4{}
\end{equation*}
The group $G$ has five irreducible representations $\rho_0, \ldots, \rho_4$ whose ranks are $1,1,2,1,1$, respectively.

As before, starting at vertex $0$.
It is only connected to vertex $2$, so we have that $B_0=\text{id}_{V_2}$ and $B^0 = \text{id}_{V_2} \otimes \alpha_0$.
% \begin{align*}
%     &B^0 = \text{id} \otimes \alpha_0 \colon V_2^\vee \longrightarrow V_2^\vee \otimes L_2^\vee.
% \end{align*}
Reinterpreting $B^0$, we get that 
$$B_2^0 \colon V_2 \otimes V_2 \xrightarrow{\det} L_2 \xrightarrow{\alpha_0} V_0.$$
So far, vertex $0$ has given us a column of $B_2$ and another of $B^2$.
These columns, the commutative diagram (\ref{eq:comdiag}) and some reflection give that $B_2^i$ for $i=1,3,4$ factors through $S^2(V_2)$.

We now turn to the vertices $i=1,3,4$.
These are only connected to vertex $2$ and so $B_i=B_i^2$ and $B^i= (B_2^i)^T$.
Furthermore, since $d_i=1$ for these vertices Equation~(\ref{eq2:cons2}) translates to $$B_i = \alpha_i \circ \Omega \circ B^i \circ \Omega.$$
This allows us to eliminate $B_i$ for $i=1,3,4$ from the problem.
What remains is:
\begin{align*}
    \bfx \colon &V_0 \longrightarrow V_2 \\
    \alpha_2 \colon & L_2 \otimes L_2 \longrightarrow L_0 \otimes L_1 \otimes L_3 \otimes L_4 \\
    \alpha_i \colon &L_i \otimes L_i \longrightarrow L_2 \\
    B_2^i \colon &S^2(V_2) \longrightarrow V_i 
\end{align*}
with $i=1,3,4$.

It is sometimes more helpful to rearrange the data $B_2^i$ to something resembling a $2 \times 2$ matrix 
$$(B_2^i)^\dagger \colon V_2 \otimes V_i^\vee \longrightarrow V_2 \otimes L_2^\vee$$
The fact that $B_2^i$ factors through $S^2(V_2)$ translates to  tracelessness of $(B_2^i)^\dagger$.
Our relations imply that
$$(B_2^3)^\dagger (B_2^4)^\dagger = \alpha_2 \alpha_3 (B_2^1)^\dagger.$$
We now sketch a direct proof of Theorem~\ref{thm:tannaka} in this case; it is where this all started.
\begin{proof}
To simplify notation we pick bases of $V_0, \ldots, V_4$, think of the fields as matrices and let $\Gamma$ act by change of basis. 
One may act by $\Gamma$ to fix the scalar fields $\alpha_i$ to $1$.
The subgroup of $\Gamma$ fixing the scalar fields at $1$ is $$\{\,(1,\gamma_1, \ldots, \gamma_4) \in \Gamma \,\,|\,\, \gamma_1^2=1,\, \gamma_3^2=1,\, \gamma_4 = \gamma_1\gamma_3,\, \det\gamma_2=1\,\} \subset \Gamma.$$

The section $(B_2^3)^\dagger$ is traceless and invertible so we may conjugate it to $\text{diag}(a, -a)$ for some $a \neq 0$.
We also have that $(B_2^3)^\dagger (B_2^4)^\dagger$ is traceless which implies that $(B_2^4)^\dagger$ is of the form $\sigma \cdot \text{diag}(b,c)$ where $b,c \neq 0$ and $\sigma$ is the nontrivial $2\times2$ permutation matrix.
The subgroup of the $\SL(V_2)$ component fixing $(B_2^3)^\dagger$ and $(B_2^4)^\dagger$ up to scalar is now precisely $G$ as presented above.
A careful calculation of how the scalars in $\Gamma$ interact with $G \subset \SL(V_4)$ reveals that they act as the rank 1 irreducible representations of $G$.
\end{proof}



\bibliographystyle{amsplain}
\bibliography{references}

\end{document}